---
title: "Final CSPS 2021 Response Rates"
date: Sys.Date()
weight: 100
summary: "Index page"
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages(library(tidyverse))

data_dir <- file.path(dirname(getwd()), "data")

overall_rate_data <- readr::read_csv(
  file.path(data_dir,"total_responses_2021.csv")
)

latest_data <- overall_rate_data %>%
   filter(is.na(end_date))

org_data <- readr::read_csv(
  file.path(data_dir, "final_org_rates.csv")
)

org_out <- org_data %>%
  select(org_group, org, name, n, rr) %>%
  mutate(
    across(c(n, rr), ~if_else(n < 10, NA_real_, .)),
    rr = if_else(rr > 1, 1, rr),
    name = if_else(is.na(n), paste0(name, "*"), name)) %>%
  arrange(desc(rr)) %>%
  select(-n)

sd_org_out <- crosstalk::SharedData$new(org_out)

fs_group <- crosstalk::filter_select(
  "fs_group",
  label = "Departmental group",
  group = ~org_group,
  sharedData = sd_org_out,
  multiple = FALSE)

fs_org <- crosstalk::filter_select(
  "fs_org",
  label = "Organisation",
  group = ~name,
  sharedData = sd_org_out,
  multiple = TRUE)

unstrap <- function(x) {
  attr(x, "html_dependencies") <-
    Filter(
      function(dependency) {dependency$name != "bootstrap"},
      attr(x, "html_dependencies")
    )
  x
}

```

<span class="govuk-body-l">The Civil Service People Survey 2021 has closed and final response rates have been confirmed. In total there were **`r prettyNum(latest_data$cumulative, big.mark=",")`** responses, this is an overall response rate of **`r scales::percent(latest_data$rr, accuracy = 0.1)`**.</span>

<hr class="govuk-section-break govuk-section-break--l">

## Final response rate by organisation

The following table shows the final response rate for each of the 101 participating departments and agencies, the median response rate across participating organisations is `r scales::percent(median(org_out$rr, na.rm = TRUE), accuracy = 0.1)`.

You can sort the table by clicking on a column heading and use the filter controls to select a departmental grouping or select specific organisations.

::::{.govuk-grid-row .data-card}

:::{.govuk-grid-column-one-quarter .filter-controls .govuk-body-s}

<span class="govuk-heading-s">Filters</span>

```{r selector, echo=FALSE}

unstrap(fs_group)

unstrap(fs_org)

```
:::

:::{.govuk-grid-column-three-quarters .tbl-display}
```{r org-table, echo=FALSE}
govukhugo::govuk_datatable(sd_org_out,
                           col_names = c("Group", "Code", "Organisation", "Response Rate"),
                           page_length = 10, 
                           search = FALSE,
                           col_defs = list(
                             list(visible = FALSE, 
                                  targets = list(0)))
                           ) %>%
  DT::formatPercentage(columns = 4, digits = 1)
```
:::

::::

<hr class="govuk-section-break govuk-section-break--xl govuk-section-break--visible">

## Notes
1. The 2021 People Survey ran from 28 September to 3 November.
1. Final response rates include paper survey respondents, during the fieldwork period only online responses were shown in this tool.
1. The acronyms provided in the code column of the table are internal codes used by the People Survey and may not relate to official acronyms used by the organisation.
1. The People Survey is not a source of official statistics on the size of Civil Service organisations, as such organisational headcounts and numbers of responses are not provided in this table. Please refer to the [Civil Service Statistics](https://www.gov.uk/government/statistics/civil-service-statistics-2021) published by the Cabinet Office and the [Public Sector Employment statistics](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/publicsectorpersonnel/bulletins/publicsectoremployment/previousReleases) published by the Office for National Statistics for the latest official statistics.
1. Some organisations invite a larger number of people working for their organisation than their official civil service headcount to complete their survey. For example, FCDO ask locally engaged staff working in overseas missions and MOD ask military staff working in civilian MOD roles to participate in the survey.

<hr class="govuk-section-break govuk-section-break--m">

<span class="govuk-body-s">Page generated: `r format(Sys.time(), "%d-%b-%Y %H:%M:%S")`</span>
