---
title: "CSPS 2021 response rate over time"
date: 2021-01-01
weight: 200
summary: "Civil Service response rate over time"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages(library(tidyverse))

data_dir <- file.path(dirname(getwd()), "data")

csps2021_rr <- readr::read_csv(file.path(data_dir, "total_responses_2021.csv")) %>%
  rename(date_2021 = end_date) %>%
  mutate(date_2021 = if_else(is.na(date_2021), 
                             as.Date("2021-11-04"), 
                             date_2021)
         )

csps2020_rr <- readr::read_csv(file.path(data_dir, "total_responses_2020.csv"))

day_compare <- tibble::tibble(
    day = c(1:37, 99),
    date_2021 = c(as.Date("2021-09-28") + 0:37)
  ) %>% 
  left_join(csps2021_rr, by = "date_2021") %>%
  left_join(csps2020_rr, by = "day") %>%
  select(day, date_2021, n_2021 = cumulative, rr_2021 = rr, n_2020, rr_2020)

latest_day <- day_compare %>%
  drop_na(rr_2021) %>%
  filter(day == max(day)) %>%
  mutate(rr_2020 = if_else(is.na(rr_2020), max(day_compare$rr_2020, na.rm = TRUE), rr_2020))

```

The Civil Service People Survey 2021 has closed and final response rates have been confirmed, the final response rate is `r scales::percent(latest_day$rr_2021, accuracy = 0.1)`, The final response rate of the 2020 survey was `r scales::percent(latest_day$rr_2020, accuracy = 0.1)`. The graph and table below shows the overall Civil Service response rate over time for 2020 and 2021.

Please note that rates for a given fieldwork day in the two years might not be directly comparable for a number of reasons, including: different start dates for the survey overall; different start dates in different departments and agencies; and, the relative position of weekends. The 2021 survey ran for two additional working days compared to the 2020 survey.


```{r rate-graph, warning=FALSE}
rate_data <- day_compare %>%
  select(date_2021, rr_2021, rr_2020) %>%
  pivot_longer(cols = c(rr_2021, rr_2020), names_to = "year", values_to = "rr") %>%
  mutate(
    year = factor(paste("CSPS", str_remove_all(year, "\\D+")), 
                  levels = c("CSPS 2020", "CSPS 2021"), ordered = TRUE),
    date_2021 = as.POSIXct(date_2021)) %>%
  drop_na(rr)

latest_data <- latest_day %>%
  mutate(higher = rr_2021 > rr_2020) %>%
  select(date_2021, rr_2021, rr_2020, higher) %>%
  pivot_longer(cols = c(-date_2021, -higher), names_to = "year", values_to = "rr") %>%
  mutate(year = str_replace(year, "rr_", "CSPS "))

latest_graph_data <- latest_data %>%
  mutate(
    year = factor(year, 
                  levels = c("CSPS 2020", "CSPS 2021"), ordered = TRUE),
    date_2021 = as.POSIXct(date_2021),
    point_size = if_else(year == "CSPS 2021", 2, 1),
    label = paste0(year, "\nFinal RR: ", 
                   scales::percent(rr, accuracy = 0.1)),
    label_x = case_when(
      year == "CSPS 2020" & higher ~ as.POSIXct(date_2021 + (6 * 60 * 60)),
      year == "CSPS 2021" & higher ~ as.POSIXct(date_2021 - (6 * 60 * 60)),
      year == "CSPS 2020" & !higher ~ as.POSIXct(date_2021 - (6 * 60 * 60)),
      year == "CSPS 2021" & !higher ~ as.POSIXct(date_2021 + (6 * 60 * 60))
    ),
    label_hjust = case_when(
      year == "CSPS 2020" & higher ~ 0,
      year == "CSPS 2021" & higher ~ 1,
      year == "CSPS 2020" & !higher ~ 1,
      year == "CSPS 2021" & !higher ~ 0
    ),
    label_vjust = case_when(
      year == "CSPS 2020" & higher ~ 1,
      year == "CSPS 2021" & higher ~ 0,
      year == "CSPS 2020" & !higher ~ 0,
      year == "CSPS 2021" & !higher ~ 1
    )
  )

rate_graph <- ggplot(rate_data, 
                     aes(x = date_2021, y = rr, 
                         colour = year, size = year, group = year)) +
  geom_label(data = latest_graph_data, 
            aes(
              x = label_x,
              label = label,
              hjust = label_hjust,
              vjust = label_vjust),
            size = 3.5,
            fill = "#ffffff",
            label.size = 0,
            show.legend = FALSE) +
  geom_line() +
  geom_point(data = latest_graph_data, 
             aes(size = as.character(point_size)), show.legend = FALSE) +
  scale_colour_manual(
    values = c("CSPS 2020" = "grey70", "CSPS 2021" = "#005abb")
  ) +
  scale_size_manual(
    values = c("CSPS 2020" = 0.5, "CSPS 2021" = 1, `1` = 1, `2` = 2),
    guide = guide_none()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     breaks = seq(0, 0.8, 0.1),
                     limits = c(0, 0.8)) +
  scale_x_datetime(
    breaks = as.POSIXct("2021-09-27") + 
      c(1, 7, 14, 21, 28, 35, 37)*86400 + 
      c(0, 0,  0,  0,  0, 3600, 3600),
    labels = scales::label_date(format = "%a %d-%b", tz = "Europe/London"),
    expand = expansion(add = c(86400, 86400 * 6))) +
  theme_minimal() +
  theme(
    text = element_text(size = 14, colour = "#000000"),
    axis.text.x = element_text(angle = 90),
    axis.title.y = element_blank(),
    axis.title.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    legend.position = "top",
    legend.title = element_blank()
  )

govukhugo::render_svg(
  rate_graph, 800, 500,
  alt_title = "Civil Service-level response rates over time", 
  alt_desc = paste("This graph shows two lines representing the overall",
                   "level response rates from the People Survey over time.",
                   "The grey line shows the 2020 response rate and the blue",
                   "line shows the 2021 response rate. A point is shown on",
                   "each graph to represent the latest day in the 2021 survey",
                   "and the equivalent day in the 2020 survey."),
  caption = "alt_title"
  )

```

<hr class="govuk-section-break govuk-section-break--l">

```{r rate-table}
out_days <- day_compare %>%
  select(date_2021, day, rr_2021, rr_2020) %>%
  arrange(-day) %>%
  mutate(
    date_2021 = if_else(
      day == 99,
      "Final response rate",
      format(date_2021, "%a %d %b %Y")
    )
  )
  

govukhugo::govuk_datatable(
  out_days,
  col_names = c("Date", "Day", "2021 response rate", "2020 response rate"),
  search = FALSE,
  buttons = FALSE
) %>%
  DT::formatPercentage(columns = c(3, 4), digits = 1)
```

<hr class="govuk-section-break govuk-section-break--xl govuk-section-break--visible">

## Notes
1. The 2021 People Survey runs from 28 September to 3 November.
1. Final response rates combine online and paper survey responses and after validation checks have been completed. Only online responses have timestamps, paper surveys are therefore only included in the calculation of the final response rate.
1. The final response rate has been given the notional value of 99 in the day column for sorting purposes.

<hr class="govuk-section-break govuk-section-break--m">

<span class="govuk-body-s">Page generated: `r format(Sys.time(), "%d-%b-%Y %H:%M:%S")`</span>
